\documentclass[a4paper, UTF8]{article}
\begin{document}
\noindent This is my \emph{first} document in \today

the difference between having $\backslash$@ or not

Carrots are good for your eyes, since they contain Vitamin A. Have you ever seen a rabbit wearing glasses?

Carrots are good for your eyes, since they contain Vitamin A\@. Have you ever seen a rabbit wearing glasses?

the difference between having $\backslash$ or not

The numbers 1, 2, 3, etc. are called natural numbers. According to Kronecker, they were made by God; all else being the work of Man.

The numbers 1, 2, 3, etc.\ are called natural numbers. According to Kronecker, they were made by God; all else being the work of Man.

I think \LaTeX is fun

I think \LaTeX\ is fun

right and left quotes in 'single quotes' and "double quotes"

right and left quotes in \lq single quotes\rq\ and \lq\lq double quotes\rq\rq

this is the first line.\\ this is the second line

this is the first line. \\[10pt] this is the second line

\begin{center}
    The \TeX nical Institute\\[0.75cm]
    Certificate
\end{center}
\noindent This is to certify that Mr.N.O. Vice has undergone a course at this institute and is qualified to be a \TeX nicain.
\begin{flushright}
    The Director\\
    The \TeX nical Institute
\end{flushright}

\textrm{roman}  {\rmfamily roman}

\textsf{sans serif}

\texttt{type writer}

\textmd{medium}

\textbf{boldface}

\textup{upright}

\textit{italic}

\textsl{slanted}

\textsc{small cap}

A polygon of three sides is called \emph{triangle} and a polygon of four sides is called \emph{quadrilateral}

\textit{A polygon of three sides is called \emph{triangle} and a polygon of four sides is called \emph{quadrilateral}}

\newpage
\begin{center}
	{\bfseries\huge The \TeX nical Institute}\\[1cm]
	{\scshape\LARGE Certificate}
\end{center}

\noindent This is to certify that Mr.N.O. Vice has undergone a course at this institute and is qualified to be a \TeX nical Expert.

\begin{flushright}
{\sffamily The Director\\
The \TeX nical Institute}
\end{flushright}

\end{document}